Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-17 manuscript/climate_sensitivity_draft.Rmd
remove crown position from table 2

Crown position--a categorical variable including dominant, co-dominant, intermediate, and suppressed--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999.

>>>>

Crown position--a categorical variable classifying trees based on exposure to sunlight--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999. Trees were classified as follows: *dominant* trees were defined as those with crowns above the general level of the canopy, *codominant* trees as those with crowns within the the canopy; *intermediate* trees as those with crowns below the canopy level, but illuminated from above; and *suppressed* as those below the canopy and receiving minimal direct illumination from above.

### 2020-07-17 manuscript/tables&figures.Rmd
remove crown position from table 2

```{r Table 2, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table2 <- read.csv("tables_figures/publication/table2_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(table2, format = "latex", booktabs = TRUE, caption = "Table 2. Summary of dependent and independent variables examined here, along with units, definitions, and sample sizes.", 
        escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variables", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 3, 19, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("tree size", 6, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("microhabitat", 8, 12, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("species' traits", 13, 19, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```

>>>>

```{r Table 2, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table2 <- read.csv("tables_figures/publication/table2_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(table2, format = "latex", booktabs = TRUE, caption = "Table 2. Summary of dependent and independent variables in our statistical models fo drought resistance, along with units, definitions, and sample sizes.", 
        escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variables", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 3, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("species' traits", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```
